---
title: "Eating Out"
author: "Connor Rice"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out. The variable name you are looking for is "eatout".
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE, warning=FALSE}
#GSS <-read_dta(file="GSS1996.dta")
GSS <- readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

There is a notable difference between the rates at which the white and other race(s) eat out based on the percentage graphical data. However it can be seen from the non-percentage data that the sample size of the non-white race(s) are significantly smaller than that of the white race.

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

The numerical data results confirm what is seen in the graphical data, there is a large percent(<10%) between the rates at which the black and the white/other race(s) eat out. However the large percent of the total people who either do or do not eat out being white confirms that the white race sample size is massively larger than the other two race(s).

```{r}
fisherXY(mydata$race,mydata$eatout, printAll = TRUE)
```

The p-values in the fisher.xy inferential

## Discussion and Conclusion



